Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2019-03-30 revised-manuscript/ms5n17-tlp-mn-180216-001.tex
Final corrections from Marcel are added revised-manuscript has the latest version without changebars

\documentclass[review]{elsarticle}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno,changebar}
%\linenumbers
\biboptions{sort&compress}
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this paper we present a novel modular probe designed for generic
microfluidic-NMR experiments. The design is based on a transmission line
detector~\cite{stripline_jan,gream_2016} using inexpensive
printed circuit board (PCB) technology. A modular design ensures that detectors of
different geometry and size can be easily exchanged.
The NMR detector (including the tuning and matching circuit) is connected to the probe
skeleton through detachable connectors. Modularity of the probe not only allows
fast optimisation of the detector but also facilitates the use of dedicated detectors
for different microfluidic devices on a single probe base.
Once the probe base is in place, additional detectors can be manufactured
within 2-3 days for less than $\sim$200 $\geneuro$.
The probe is optimised for proton detected double resonance, with the
second channel tunable to different nuclei such as $^{13}$C, $^{15}$N, or
$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials
such as aluminium profiles of standard size, with only a small number of
custom-machined parts holding the structure together.
Detailed construction drawings and a complete set of CAD files is
available for download at \url{https://github.com/marcel-utz/modular-microfluidic-probe}.
The planar geometry of the detector accommodates exchangeable microfluidic devices
which can be designed freely for specific experimental requirements as long as the
overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative positioning.

In the remainder of this paper, we discuss the probe design in more detail,
and characterise its performance in terms of sensitivity and resolution.
We also demonstrate its application in microfluidic cell culture,
protein NMR spectroscopy, and micro-imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\cbstart
\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png}
\caption{Drawings of the detector assembly and the microfluidic device (1). A: front view; B: exploded view. Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes. In A, PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3. Thickness of each of the PCB planes is 1.52 mm and the copper layers on the PCBs is 35 $\mu$m. Both the microfluidic device and the spacer are made from PMMA and have thickness of 0.9 mm and 1 mm respectively.}
\label{fig:rf-device-assembly}
\end{figure}
\cbend
%\begin{figure}
%\centering
%\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png}
%\caption{The probe with and without sleeve.}
%\label{fig:probe}
%\end{figure}
The probe assembly design is based on readily and easily available materials and parts
with minimal need for customised fabrication.
All mechanical and electronic components are readily available from commercial sources,
with the exception of a small number of precision-machined parts which are used
to hold the assembly together. These can be ordered from commercial prototyping
manufacturers or machined in-house if mechanical workshop facilities are available.

\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png}
\caption{Exploded view of the probe design (left) and assembled probe (right).
Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 7) provides a
generic mounting point for the NMR detector assembly (red).
A microfluidic device (1) can be inserted from the top of the probe.
The device is held in place by a spacer (4) between the detector planes (3 and 5)
ensuring alignment of the sample chamber with the sensitive area on the PCB planes.
The modular NMR detector is made up of parts 3,4 and, 5 and is
connected to the TMPCB (7) through standard coaxial (SMP) connectors.
The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (9)
and, auxiliary support disks (12).}
\label{fig:probe-explode}
\end{figure}

@@

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with
precision machined parts at both ends (scaffold support disks (9)).\cbstart
The semi-rigid cables (RG 402, 50~$\Omega$) are  threaded through these hollow aluminium tubes
to reach the detector assembly.\cbend
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly.
In our case, these were laser cut from 5~mm thick poly(methyl methacrylate) (PMMA) sheets,
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 7) is held in place on the top of the probe skeleton by
the detector support rods (8), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permanently fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly. \cbstart\  It also provides
trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend
 The detector assembly is connected to the TMPCB through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}). \cbstart SMP Connector Receptacle Male Pin ($J_3$ and $J_4$ in \fig{fig:circuit}) is soldered on the TMPCB and SMP Connector Jack Male Pin is soldered on the PCB plane 3 ($J_1$ and $J_2$ in \fig{fig:circuit}). The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend
While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for
fine tuning and matching
at the magnet through tuning rods (10) which reach all the way to the probe base.

The base, the scaffold assembly and the tuning and matching PCB all have a free circular
axial bore providing access from the bottom of the probe, which can be used for
temperature and environmental control and/or fluidic connections to the sample as
needed. The detector assembly is made up of two PCBs (3 and 5) and a spacer (4) between them. \cbstart The spacer is made from a 1 mm thick PMMA sheet.\cbend  The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper
planes, each with a constriction at the centre.  This geometry gives rise to an
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field
and the detection sensitivity
onto the sample area.
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown in~\fig{fig:probe-explode}) is fixed to the auxiliary disk (2)
and the scaffold assembly with screws.
An exchangeable microfluidic device (1) can be inserted from the top of the detector.
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ.\cbstart The device inlet and outlet are sealed by an optical adhesive film (MicroAmp, AB Applied Biosystems)
when using the device as passive sample holder.\cbend
 The microfluidic device is held in place by the spacer
between the two PCB planes coinciding the sample chamber with the constriction on the
detector.  The 45-degree edges of the device outline help with precise and reliable
alignment.
Since the detector assembly is attached to the probe base through SMP
connectors, it can easily be exchanged.
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.

\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (13) for X channel.
O.D. of A is 44.45 mm and B is 38 mm. Circuit elements of X channel are integrated on the
PCB in B making it compact. Detachable SMP connectors (14) are used to
connect the RF insert (13) and the detector assembly.}
\label{fig:ProbePhoto}
\end{figure}
\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (13)
for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 13.
However, in (B) the circuitry of the RF insert (13) is integrated on the PCB plane (5),
making the design more compact.
 Probe (A) is compatible with a Varian 600 Premium shielded 14.1 T magnet, with an outer diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an
O.D. of 38 mm including the sheath, is designed to fit inside a
Bruker narrow bore shim stack.
Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with
wide bore magnets with spacers or gradient stack to keep the probe centred.

Microfluidic devices are made from inexpensive PMMA sheets by laser cutting and
thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}. \cbstart Magnetic susceptibility value of PMMA and other materials in given in table~\ref{tab:susceptibility}\cbend
Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
are cut into the middle layer. The fluidic network on the device can be designed
freely as long as the overall shape of the device is preserved, and the location
of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirements. \cbstart \fig{fig:device} shows various microfluidic devices.\cbend
\cbstart
\begin{table}[h]
\centering
\caption{Magnetic susceptibility values of the materials used in the probe\cite{wapler-2014,schenck-1996}}
\label{tab:susceptibility}
\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}||}
\hline
Material   & $\chi$/ppm	\\
\hline
PMMA		&-9.054	\\
Copper	&-9.63	\\
FR4	&-3.743		\\
Aluminium	&20.7	\\
\hline
\end{tabular}
\end{table}
\cbend
\cbstart
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png}
\caption{Microfluidic devices for different applications compatible with the current setup.
From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow,
hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and,
to grow cells on the device.}
\label{fig:device}
\end{figure}
\cbend

@@

Tuning is achieved by $L_1$ and $C_4$, which are both located on the exchangeable insert (13), in combination with

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe. The background colour relates the different circuit elements on different PCBs. The back side of the PCB plane 5 and the front side of the PCB plane 3 is shown in horizontal orientation. The front side of the TMPCB 7 is shown in vertical orientation. Trimmer capacitor $C_6$ is placed on the back side of PCB plane 5. The copper layer is shown in brown and the solder pads to place the circuit elements are shown in off-white. An insulating solder mask layer over the copper layer prevents accidental short-circuiting.

@@

including semi-rigid transmission lines were purchased from DigiKey Ltd \cbstart and Farnell element14, UK. Sodium acetate and $^{15}$N labeled urea were purchased from sigma-aldrich, UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\cbend Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment

@@

engraving system  (HPC Laser L3040), and then bonded using the protocol

@@

The precise dimensions of the detector were optimised for a given sample volume
using finite element calculations in COMSOL, as described in \cite{gream_2016}.
The RF response of the probe circuit was simulated using a symbolic network
analysis code~\cite{gream-thesis} in order to estimate appropriate component
values. Final tuning was done by trial and error using an Agilent FieldFox 4 GHz
network analyser. PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) for
manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited
resolution to about 10 Hz. A high-quality Teflon-based RF PCB material (RO3035,
Rogers Corp., USA) was therefore used for optimal performance in both
sensitivity and resolution (\fig{fig:ProbePhoto}(B)). The probe skeleton was
assembled from prefabricated aluminium tubes held with the precision-machined
scaffold disks using brass screws. Semi-rigid transmission lines were then
threaded through the tubes, and the TMPCB plate was soldered on top. The
detector planes (3 and 5) and the PMMA spacer between them were assembled using
short bits of 0.5~mm \cbstart diameter copper wire bought from RS components, UK, \cbend which were soldered to the appropriate pads in the four corners of the detector structure.

\cbstart
\subsection{Details of NMR and MRI measurements}
NMR experiments were performed on a Varian VNMRS console attached to a Varian 600 premium shielded 14.1 T magnet. Field maps in the \fig{fig:field map} were created by gradient echo (FLASH) pulse sequence with echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms on a sample of 130 mM  sodium acetate dissolved in H$_2$O. The peak shown in the \fig{fig:1H-nutation} is of H$_2$O in an aqueous solution of 100~mM $^{15}$N-urea. \fig{fig:lineshape} shows proton spectrum of the acetate resonance from 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O. The spectrum was recorded after presturating the water signal with rf-field of 100~Hz. 32 transients were averaged with a repetition delay of 3~s. The proton spectrum of DMEM (Dulbecco
modified Eagle's medium) cell growth medium in \fig{fig:media-spec} was acquired with 256 scans in 20 mins.
The left panel of \fig{fig:HSQC} shows a $^{13}$C-$^{1}$H heteronuclear single
quantum correlation (HSQC) spectrum, acquired in 12 mins (32 t$_1$ increments
and 16 scans) from a 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in
water. The right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400
mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM
$^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7.

For MRI experiments precision-cut murine liver slices (PCLS) were obtained by first extracting a
tissue core of 8 mm diameter using a biopsy punch. PCLS of 250-300 $\mu$m
thickness were cut from the core using a Krumdieck Tissue slicer, and then
reduced to 3~mm diameter using a smaller punch. The slices were incubated in
well-plates at 37$^\circ$C and 80\% O\textsubscript{2}, 5\% CO\textsubscript{2}
for 2 hours before imaging. Imaging experiments were performed on Bruker
AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet. The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness of the tissue \fig{fig:tisli}(C) shows a
RARE image using the same parameters, with 8 echos acquired per scan, thus
reducing the acquisition time to 8 minutes. A spin echo image is shown in
\fig{fig:tisli}(D), acquired over 25~min. Finally, \fig{fig:tisli}(E) shows a
$B_0$ field map, which has been obtained by acquiring two separate FLASH images
with echo times $t_E=5.3$~ms and 15.3~ms, respectively.
\cbend

@@

\begin{figure}
\centering
\includegraphics[width=.80\linewidth,keepaspectratio=true]{./figures/lineshape.png}
\caption{Spectrum of 130 mM sodium acetate dissolved in water acquired in 32 scans with water presaturation. Carbon satellites can be seen in the expanded base of the acetate line. The orange curve shows a lorentzian lineshape with full width at half maximum of 3.35 Hz.}
\label{fig:lineshape}
\end{figure}

>>>>

\documentclass[preprint,5p]{elsarticle}
\usepackage{graphicx,amssymb,amsmath,amstext,hyperref,graphics,float,eurosym,geometry,lineno,changebar}
%\linenumbers
\nochangebars
\biboptions{sort&compress}
\hypersetup{
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,         % color of internal links (change box color with linkbordercolor)    https://www.sharelatex.com/learn/Hyperlinks
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black           % color of external links
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this paper we present a novel modular probe designed for generic
microfluidic NMR experiments. The design is based on a transmission line
detector~\cite{stripline_jan,gream_2016} using inexpensive
printed circuit board (PCB) technology. A modular design ensures that detectors of
different geometry and size can be easily exchanged.
The NMR detector (including the tuning and matching circuit) is connected to the probe
skeleton through detachable connectors. Modularity of the probe not only allows
fast optimisation of the detector but also facilitates the use of dedicated detectors
for different microfluidic devices on a single probe base.
Once the probe base is in place, additional detectors can be manufactured
within 2-3 days for less than $\sim$200 $\geneuro$.
The probe is optimised for proton detected double resonance, with the
second channel tunable to different nuclei such as $^{13}$C, $^{15}$N, or
$^{31}$P. The probe skeleton is made almost entirely from easily obtainable raw materials
such as aluminium profiles of standard size, with only a small number of
custom-machined parts holding the structure together.
Detailed construction drawings and a complete set of CAD files is
available for download at \url{https://github.com/marcel-utz/modular-microfluidic-probe}.
The planar geometry of the detector accommodates exchangeable microfluidic devices
which can be designed freely for specific experimental requirements as long as the
overall shape of the device is maintained. \fig{fig:rf-device-assembly} shows the microfluidic device and the detector with their relative positioning.

In the remainder of this paper, we discuss the probe design in more detail,
and characterise its performance in terms of sensitivity and resolution.
We also demonstrate its application in microfluidic cell culture,
protein NMR spectroscopy, and micro-imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\cbstart\
\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/fig1-ms5n17-tlp-im-190205-rf-device-assembly.png}
\caption{Drawings of the detector assembly and the microfluidic device (1). A: front view (dimensions in mm); B: exploded view. Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes. In A, PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3. Thickness of each of the PCB planes is 1.52 mm and the copper layers on the PCBs is 35 $\mu$m. Both the microfluidic device and the spacer are made from PMMA and have thickness of 0.9 mm and 1 mm respectively.}
\label{fig:rf-device-assembly}
\end{figure}
\cbend\
%\begin{figure}
%\centering
%\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png}
%\caption{The probe with and without sleeve.}
%\label{fig:probe}
%\end{figure}
The probe assembly design is based on readily and easily available materials and parts
with minimal need for customised fabrication.
All mechanical and electronic components are readily available from commercial sources,
with the exception of a small number of precision-machined parts which are used
to hold the assembly together. These can be ordered from commercial prototyping
manufacturers or machined in-house if mechanical workshop facilities are available.

\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/fig2-ms5n17-tlp-im-181007-Probe-explode.png}
\caption{Exploded view of the probe design (left) and assembled probe (center).
Probe base (blue) and scaffold assembly (green) with TMPCB (brown, 7) provides a
generic mounting point for the NMR detector assembly (red).
A microfluidic device (1) can be inserted from the top of the probe.
The device is held in place by a spacer (4) between the detector planes (3 and 5)
ensuring alignment of the sample chamber with the sensitive area on the PCB planes.
The modular NMR detector is made up of parts 3,4 and, 5 and is
connected to the TMPCB (7) through standard coaxial (SMP) connectors.
The scaffold assembly is made up of aluminium tubes (11), scaffold support disks (9)
and, auxiliary support disks (12).}
\label{fig:probe-explode}
\end{figure}

@@

The scaffold assembly is made up of two hollow aluminium tubes (11) held together with
precision machined parts at both ends (scaffold support disks (9)).\cbstart\ The semi-rigid cables (RG 402, 50~$\Omega$) are  threaded through these hollow aluminium tubes
to reach the detector assembly.\cbend\
Auxiliary support disks (12) provide additional rigidity for the scaffold assembly.
In our case, these were laser cut from 5~mm thick poly(methyl methacrylate) (PMMA) sheets,
but they may also be made by conventional machining.
A tuning and matching PCB (TMPCB, 7) is held in place on the top of the probe skeleton by
the detector support rods (8), with the semi-rigid coaxial cables providing
additional support.
The TMPCB is permanently fixed to the probe base, and serves as attachment point
for the exchangeable detector assembly.\cbstart\ It also provides
trimmer capacitors (6) for secondary tuning and matching of the detector.\cbend\ The detector assembly is connected to the TMPCB through a pair of
low-loss SMP connectors (14 in \fig{fig:ProbePhoto}). \cbstart\ The SMP connector receptacle male pin ($J_3$ and $J_4$ in \fig{fig:circuit}) is soldered on the TMPCB and the SMP connector jack male pin is soldered on the PCB plane 3 ($J_1$ and $J_2$ in \fig{fig:circuit}). The TMPCB and 3 are connected by a coaxial connector SMP plug adapter.\cbend\ While each detector assembly is roughly
tuned and matched with fixed circuit elements soldered onto it,
the adjustable capacitors on the TMPCB are used for
fine tuning and matching
at the magnet through tuning rods (10) which reach all the way to the probe base.

The base, the scaffold assembly and the tuning and matching PCB all have a free circular
axial bore providing access from the bottom of the probe, which can be used for
temperature and environmental control and/or fluidic connections to the sample as
needed. The detector assembly is made up of two PCBs (3 and 5) and a spacer (4) between them.\cbstart\ The spacer is made from a 1 mm thick PMMA sheet.\cbend\ The detector used here is based on a planar transmission line geometry as described elsewhere~\cite{gream_2016,stripline_jan}; other structures such as spiral
coils and Helmholtz pairs are also possible, and can easily be realised on a PCB.
The transmission line detector consists of a pair of copper
planes, each with a constriction at the centre.  This geometry gives rise to an
electromagnetic eigenmode with a strong anti-node of the magnetic field between
the two planes at the site of the constriction. This concentrates the rf field
and the detection sensitivity
onto the sample area.
The shape and size of the copper structures have been chosen such as to produce
an eigenfrequency of this mode around 630~MHz. The PCBs have been designed with
solder points at the back side for chip capacitors; these can be used to tune the
resonance down to the desired proton Larmor frequency (500 or 600~MHz in the present case).
Both the PCBs (3 and 5) also carry circuitry for channel separation and primary
matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs
together at the top, and forms the top end of the probe assembly.
The probe sheath (not shown in~\fig{fig:probe-explode}) is fixed to the auxiliary disk (2)
and the scaffold assembly with screws.
An exchangeable microfluidic device (1) can be inserted from the top of the detector.
Microfluidic devices can be used as passive sample holders, filled before putting them
into the probe,
or the device can be actively perfused and operated in-situ.\cbstart\ The device inlet and outlet are sealed by an optical adhesive film (MicroAmp, AB Applied Biosystems)
when using the device as passive sample holder.\cbend\ The microfluidic device is held in place by the spacer
between the two PCB planes coinciding the sample chamber with the constriction on the
detector. The 45-degree edges of the device outline help with precise and reliable
alignment.
Since the detector assembly is attached to the probe base through SMP
connectors, it can easily be exchanged.
Using standard PCB processes to manufacture the detector provides great flexibility
to optimise detector performance for different applications, including different
microfluidic sample sizes, and different combinations of target nuclei.

\begin{figure}
\centering
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/fig3-ms5n17-tlp-im-181007-both-detectors.png}
\caption{Dual channel probes with (A) and without (B) modular RF insert (13) for X channel.
O.D. of A is 44.45 mm and B is 38 mm. Circuit elements of X channel are integrated on the
PCB in B making it compact. Detachable SMP connectors (14) are used to
connect the RF insert (13) and the detector assembly.}
\label{fig:ProbePhoto}
\end{figure}
\fig{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (13)
for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging (13).
However, in (B) the circuitry of the RF insert (13) is integrated on the PCB plane (5),
making the design more compact.
 Probe (A) is compatible with a Varian 600 Premium shielded 14.1 T magnet, with an outer diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an
O.D. of 38 mm including the sheath, is designed to fit inside a
Bruker narrow bore shim stack.
Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with
wide bore magnets with appropriate spacers to keep the probe centered.

The microfluidic devices were made from inexpensive PMMA sheets by laser cutting and
thermal bonding, as described in detail elsewhere \cite{yilmaz_bonding}.\cbstart\ PMMA was chosen for ease of fabrication, but also due to the close match in magnetic susceptibility with that of water (Table~\ref{tab:susceptibility}).\cbend\
Briefly, the devices consist of a 0.5~mm thick middle layer between a  top and
bottom layer of 0.2~mm thickness each. The sample chamber and fluidic network
are cut into the middle layer. The fluidic network on the device can be designed
freely as long as the overall shape of the device is preserved, and the location
of the sample chamber is maintained. The volume of the sample chamber is 2.5~$\mu$l which can be increased or decreased according to the experimental requirements. \cbstart \fig{fig:device} shows various microfluidic devices.\cbend
\cbstart
\begin{table}[h]
\centering
\caption{Magnetic susceptibility values of some relevant materials.\cite{wapler-2014,schenck-1996}}
\label{tab:susceptibility}
\begin{tabular}{||p{.3\linewidth}|p{.3\linewidth}||}
\hline
Material   & $\chi$/ppm	\\
\hline
PMMA		&-9.054	\\
Copper	&-9.63	\\
FR4	&-3.743		\\
Aluminium	&20.7	\\
Water & -9.02\\
\hline
\end{tabular}
\end{table}
\cbend
\cbstart
\begin{figure}
\centering
\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/fig4-ms5n17-tlp-im-181007-devices.png}
\caption{Microfluidic devices for different applications compatible with the current setup.
From left: Devices for perfusion of tissue slice on a chip, peristaltic pumping to induce flow,
hydrogenation on a chip, droplet generator, simple design to fill the sample chamber and,
to grow cells on the device.}
\label{fig:device}
\end{figure}
\cbend

@@

Tuning is achieved by $L_1$ and $C_4$ in combination with

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/fig5-ms5n17-tlp-im-180110-circuit-diagram.png}
\caption{Circuit diagram of the double resonance probe. The background colour relates the different circuit elements on different PCBs. The back side of the PCB plane 5 and the front side of the PCB plane 3 is shown in horizontal orientation. The front side of the TMPCB 7 is shown in vertical orientation. Trimmer capacitor $C_6$ is placed on the back side of PCB plane 3. The copper layer is shown in brown and the solder pads to place the circuit elements are shown in off-white. An insulating solder mask layer over the copper layer prevents accidental short-circuiting.

@@

including semi-rigid transmission lines were purchased from DigiKey Ltd\cbstart\ and Farnell element14, UK. Sodium acetate and $^{15}$N labeled urea were purchased from Sigma-Aldrich, UK and Dulbecco Modified Eagle's Medium (DMEM) supplemented was purchased from Life Technologies, USA.\cbend\ Cell cast PMMA sheets for microfluidic devices were bought from Weatherall Equipment

@@

engraving system  (L3040 from HPC Laser LTD, Elland, UK), and then bonded using the protocol

@@

The precise dimensions of the detector were optimised for a given sample volume
using finite element calculations in COMSOL, as described in \cite{gream_2016}.
The RF response of the probe circuit was simulated using a symbolic network
analysis code~\cite{gream-thesis} in order to estimate appropriate component
values. Final tuning was done by trial and error using an Agilent FieldFox 4 GHz
network analyser. PCB layouts were designed using KiCAD, and then sent to
beta-layout GmbH (Aarbergen, Germany) and P.W. Circuits Ltd.~(Wigston, UK) for
manufacturing. Easily and inexpensively available FR4 PCB material
(\fig{fig:ProbePhoto}(A)) proved adequate for some purposes, but limited
resolution to about 10 Hz. A high-quality Teflon-based RF PCB material (RO3035,
Rogers Corp., USA) was therefore used for optimal performance in both
sensitivity and resolution (\fig{fig:ProbePhoto}(B)). The probe skeleton was
assembled from prefabricated aluminium tubes held together with the precision-machined
scaffold disks using brass screws. Semi-rigid transmission lines were then
threaded through the tubes, and the TMPCB plate was soldered on top. The
detector planes (3 and 5) and the PMMA spacer between them were assembled using
short bits of 0.5~mm\cbstart\ diameter copper wire bought from RS components, UK,\cbend\ which were soldered to the appropriate pads in the four corners of the detector structure.

\cbstart
\subsection{Details of NMR and MRI measurements}
NMR spectra were obtained on a Varian VNMRS console attached to a Varian 600 premium shielded 14.1 T magnet. Field maps in the \fig{fig:field map} were created by gradient echo (FLASH) pulse sequence with echo times ($t_{e}$) of 6 and 16 ms and repetition time ($t_{r}$) of 100 ms on a sample of 130 mM  sodium acetate dissolved in H$_2$O. The peak shown in the \fig{fig:1H-nutation} is of H$_2$O in an aqueous solution of 100~mM $^{15}$N-urea. \fig{fig:lineshape} shows proton spectrum of 2.5 $\mu$l of 130 mM  sodium acetate dissolved in H$_2$O. The spectrum was recorded after pre-saturating the water signal at a nutation frequency of 100~Hz. 32 transients were averaged with a repetition delay of 3~s. The proton spectrum of DMEM (Dulbecco
modified Eagle's medium) cell growth medium in \fig{fig:media-spec} was acquired with 256 scans in 20 mins.
The left panel of \fig{fig:HSQC} shows a $^{13}$C-$^{1}$H heteronuclear single
quantum correlation (HSQC) spectrum, acquired in 12 mins (32 t$_1$ increments
and 16 scans) from a 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in
water. The right panel shows a $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400
mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM
$^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7.

For MRI experiments precision-cut murine liver slices (PCLS) were obtained by first extracting a
tissue core of 8 mm diameter using a biopsy punch. PCLS of 250-300 $\mu$m
thickness were cut from the core using a Krumdieck Tissue slicer, and then
reduced to 3~mm diameter using a smaller punch. The slices were incubated in
well-plates at 37$^\circ$C and 80\% O\textsubscript{2}, 5\% CO\textsubscript{2}
for 2 hours before imaging. Imaging experiments were performed on a Bruker
AVANCE III spectrometer on a Bruker Active Shield II wide bore 11.7 T magnet equipped with a Bruker Micro2.5 gradient system. The image shown in \fig{fig:tisli}(B) was acquired using a FLASH pulse sequence with $t_R=120$~ms and $t_E=15.3$~ms. The slice thickness of  1~mm encompasses the entire thickness of the tissue. \fig{fig:tisli}(C) shows a
RARE image using the same parameters, with 8 echos acquired per scan, thus
reducing the acquisition time to 8 minutes. A spin echo image is shown in
\fig{fig:tisli}(D), acquired over 25~min. Finally, \fig{fig:tisli}(E) shows a
$B_0$ field map, which has been obtained by acquiring two separate FLASH images
with echo times $t_E=5.3$~ms and 15.3~ms, respectively.
\cbend

@@

\begin{figure}
\centering
\includegraphics[width=.80\linewidth,keepaspectratio=true]{./figures/fig9-lineshape.png}
\caption{Spectrum of 130 mM sodium acetate dissolved in water acquired in 32 scans with water presaturation. Carbon satellites can be seen in the expanded base of the acetate line. The orange curve shows a lorentzian lineshape with full width at half maximum of 3.35 Hz.}
\label{fig:lineshape}
\end{figure}
